---
title: "R Project 1 - Hello R"
author: "Vanessa Perez"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The Dino data should have 3 columns and 1846 rows. The dataset, x, and y variables. 

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Star Data:

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Star Data Correlation:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
 


### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)


```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
  
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```


